Roster Review (Generic)

### 2019-06-07 rosterReview_generic.Rmd
Reordering research in generic rmd

```{r}
force <- TRUE
force_all <- FALSE
batter_file <- "temp/FanGraphs Leaderboard.csv"
pitcher_file <- "temp/FanGraphs Leaderboard (1).csv"

@@

```{r}
# TODO find way to wrap these three views into one
rosters %>% 
  filter(grepl("Plouffe|Matter",team)) %>% 
  select(team, manager, name_full, display_position, zar, positions) %>% 
  arrange(zar %>% desc) %>% 
  View()
  # mutate(zar = janitor::round_half_up(zar)) %>% 
  # write_csv("data/tradeReview_20190423.csv")

rosters %>% 
  filter(grepl("Plouffe|Matter",team)) %>% 
  ggplot(aes(x=team,y=zar,color=type)) +
  geom_jitter(aes(text=glue("{name_full} - {display_position}", color=type)), width=.2) +
  coord_flip() -> tv

rosters %>% 
  filter(grepl("Plouffe|Matter",team)) %>% 
  select(team, manager, name_full, display_position, zar) %>% 
  filter(grepl("Hicks|Muncy",name_full)) 
# %>%
#   group_by(team) %>%
#   summarize(zar = sum(zar))
```

@@

team_pos_avg_zar %>% 
  ungroup() %>% 
  group_by(team) %>% 
  summarize(avg_pos_zar = mean(avg_pos_zar)) %>% 
  arrange(avg_pos_zar %>% desc)
```

>>>>

```{r}
force <- TRUE
force_all <- TRUE
batter_file <- "temp/FanGraphs Leaderboard.csv"
pitcher_file <- "temp/FanGraphs Leaderboard (1).csv"

@@

@@

team_pos_avg_zar %>% 
  ungroup() %>% 
  group_by(team) %>% 
  summarize(ovrl_avg_pos_zar = mean(avg_pos_zar),
            var_pos_zar = sd(avg_pos_zar)) %>% 
  arrange(ovrl_avg_pos_zar %>% desc)

rosters_by_position %>% 
  filter(team != "Free Agent") %>% 
  ggplot(aes(pos_zar)) + 
  geom_freqpoly(binwidth=.25) + 
  facet_wrap(~ position)
```

```{r}
# TODO find way to wrap these three views into one
rosters %>% 
  filter(grepl("Plouffe|Nuts",team)) %>% 
  select(team, manager, name_full, display_position, zar, positions) %>% 
  arrange(zar %>% desc) %>% 
  View()
  # mutate(zar = janitor::round_half_up(zar)) %>% 
  # write_csv("data/tradeReview_20190423.csv")

rosters %>% 
  filter(grepl("Plouffe|Nuts",team)) %>% 
  ggplot(aes(x=team,y=zar,color=type)) +
  geom_jitter(aes(text=glue("{name_full} - {display_position}", color=type)), width=.2) +
  coord_flip() -> tv

rosters %>% 
  #filter(grepl("Plouffe|Oakmont|Nuts",team)) %>% 
  select(team, manager, name_full, display_position, zar) %>% 
  filter(grepl("Benintendi|Martin Perez",name_full)) 
# %>%
#   group_by(team) %>%
#   summarize(zar = sum(zar))
```
